Abstractions and exemplars: the measure noun phrase alternation in German

### 2018-05-30 Latex/sections/3corpus.tex
Final final final touches.

For this pre-study, each of the 2,365 combinations of measure noun lemma and kind noun lemma were queried in the \NACb\ and the \PGCd\ with a limit of 100 randomly chosen results for each single query.%
\footnote{The data package for this paper (including all concordances and R scripts) is made available under the DOI \doi{10.5281/zenodo.1254871}.}
From the resulting 35,766 sentences, 5,000 were randomly sampled for the statistical analysis.
All features described in Section~\ref{sec:variablesandannotation} were annotated except for the ones which do not apply in the non-alternating case (\textit{Kindattraction}, \textit{Measureattraction}, and \textit{Measurecase}).

>>>>

For this pre-study, each of the 2,365 combinations of measure noun lemma and kind noun lemma were queried in the \NACb\ and the \PGCd\ with a limit of 100 randomly chosen results for each single query.%
\footnote{The data package for this paper (including all concordances and R scripts) is made available under the following DOI\slash URL: \url{https://dx.doi.org/10.5281/zenodo.1254871}.}
From the resulting 35,766 sentences, 5,000 were randomly sampled for the statistical analysis.
All features described in Section~\ref{sec:variablesandannotation} were annotated except for the ones which do not apply in the non-alternating case (\textit{Kindattraction}, \textit{Measureattraction}, and \textit{Measurecase}).
